### 2013-10-07 discussion.tex
updated

\section{Discussion}\label{sect:discussion}

This study was designed to compared the zonal anatomy of the prostate in
patients with biopsy-proven PCa as seen in ARFI imaging and MR T2WI.  Overall,
ARFI imaging performed well when compared with MR estimates of total and
central gland volume (Figure~\ref{fig:mr_arfi_volumes}), though ARFI tended to
overestimate prostate total gland volume, most commonly due to over-estimation
of the anterior-to-posterior dimension of the prostate.  As seen in Figure XX,
clear delineation of the anterior aspect of the prostate can be challenging in
ARFI and B-mode images due to poor SNR, since this is the deepest aspect of the
prostate relative to the rectal wall imaging surface. MR T2WI can also have
difficulties visualizing and diagnosing lesions in the anterior region of the
prostate,~\cite{Gupta2013}, which is thought to be secondary to the
heterogeneity of the gland in that area, especially in the presence of BPH.
This was evident in imaging study subject 4, with a $\sim$143 g prostate
(Figure~\ref{fig:mr_arfi_weight}), which was an outlier in terms of weight and
volume.  With study subject 4 excluded, MR and ARFI imaging volumes and the
ellipsoidal prostate volume estimates had similar correlation with prostate
weights (Figure~\ref{fig:mr_arfi_weight}(d)).

The most accurate measurements for both the total prostate gland and central
gland were in the lateral-to-lateral dimension
(Figure~\ref{fig:mr_arfi_path_axes}(a), Table~\ref{tab:mr_arfi_axes_error}),
with ARFI imaging exhibiting a slight overestimate in both glands.  ARFI
imaging had weaker correlations with MR imaging in the apex-to-base dimension
(Figure~\ref{fig:mr_arfi_path_axes}(c)), though it should be noted that the MR
images are limited in spatial resolution by slice thickness and volume
averaging in this dimension ($\sim$ 3 mm).  Finally, as expected from
qualitative image evaluation, the anterior-to-posterior dimension had the
weakest correlations, especially in the central gland, most likely related to
the inability to clearly resolve an anterior border for both the prostate total
and central glands. Of note, a slight overestimation of anatomic borders can
result in a large relative difference from the true values (by histology) as the gland
is small in size.

@@

Future directions for our research include deeper analysis of our findings,
especially the lateral-to-lateral overestimation, in order to improve our
anatomic delineation and assess further its clinical impact. Although work
remains to be done, the fact that one can view the different prostatic zones on
ARFI images in addition to MRI is encouraging and could lead to targeted
diagnostic biopsies and therapies with real-time imaging for men with PCa.

>>>>

\section{Discussion}\label{sect:discussion}
This study was designed to compared the zonal anatomy of the prostate in
patients with biopsy-proven PCa as seen in ARFI imaging and MR T2WI.  Overall,
ARFI imaging performed well when compared with MR estimates of total and
central gland volume (Figure~\ref{fig:mr_arfi_volumes}), though ARFI tended to
overestimate prostate total gland volume, most commonly due to over-estimation
of the lateral dimension of the prostate.  This can be due to poor contrast
between the PZ and peri-prostate fat (Figure~\ref{fig:arfi_segs}).  As seen in
Figure~\ref{fig:arfi_segs}, clear delineation of the anterior aspect of the
prostate can also be challenging in ARFI and B-mode images due to poor SNR,
since this is the deepest aspect of the prostate relative to the rectal wall
imaging surface. MR T2WI can also have difficulties visualizing and diagnosing
lesions in the anterior region of the prostate,~\cite{Gupta2013}, which is
thought to be secondary to the heterogeneity of the gland in that area,
especially in the presence of BPH.  This was evident in imaging study subject
4, with a $\sim$143 g prostate (Figure~\ref{fig:mr_arfi_weight}), which was an
outlier in terms of weight and volume.  The most accurate measurements for both
the total prostate gland and central gland were in the apex-to-base dimension
(Figure~\ref{fig:mr_arfi_path_axes}(c), Table~\ref{tab:mr_arfi_axes_error}),
with no mean bias in ARFI imaging estimates, but significant case-to-case
variability, leading to poor linear regression coefficients of determination.

@@

It should also be noted that this study did not evaluate user biases in image
segmentation.  While MR zonal anatomy delineation has some establishment in the
clinical literature, this study is the first attempt to define the criteria for
ARFI imaging zonal anatomy characteristics, and it is expected that such
delineations will continue to be refined as we acquire more cases and continue
to compare with MRI and pathology data.  Given this limitation, no attempts
were made to further quantify reader-to-reader variability in this work.

Future directions for our research include deeper analysis of our findings,
especially the lateral dimension over-estimation, to improve our anatomic
delineation and assess further its clinical impact.  Technological improvements
to improve anterior prostate boundary delineation in both B-mode and ARFI
imaging are also being pursued and will hopefully allow for the currently
elusive anterior PCa lesions in MR to be seen in ARFI imaging.  Although work
remains to be done, the fact that one can view the different prostatic zones on
ARFI images in addition to MRI is encouraging and could lead to targeted
diagnostic biopsies and therapies with real-time imaging for men with PCa.

### 2013-10-07 results.tex
updated

Weights and axis measurements from the gross pathology processing of the
excised prostates were collected (Table~\ref{tab:path_data}), and using the
axis measurements (lateral-to-lateral, anterior-to-posterior, and
apex-to-base), the prostate volume was approximated as a tri-axial ellipsoid,
and its volume was estimated (\ref{eqn:ellipsoid_volume}).  Prostate weights
were moderately correlated with estimated pathology ellipsoidal prostate
volumes (Figure~\ref{fig:mr_arfi_weight}(a), R$^2$ = 0.68).  There was moderate
correlation between the prostate weight and the image-reconstructed prostate
volumes (Figure~\ref{fig:mr_arfi_weight}(b), R$^2$ = 0.44 (MR) and 0.21
(ARFI)), though there was weaker correlation with the ellipsoidal approximation
of the measurement prostate volume and the image-reconstructed volumes
(Figure~\ref{fig:mr_arfi_weight}(c), R$^2$ = 0.08 (MR) and 0.01 (ARFI)).  Study
subject \#4 had a very large prostate, which could not be completely captured
in MR or ARFI imaging in the anterior region, so the same analyses were
performed with that study subject excluded
(Figure~\ref{fig:mr_arfi_weight}(d-e)), improving correlations for MR and ARFI
to the prostate weights (R$^2$ = 0.74 and 0.60, respectively), and prostate
volumes (R$^2$ = 0.39 for both imaging modalities).

@@

Measurements of the prostate total and central gland dimensions along the three
standard anatomic axes (apex-to-base, lateral-to-lateral, and
anterior-to-posterior) were made (Table~\ref{tab:mr_arfi_axes}), and the
correlation between the imaging axis measurements was analyzed
(Figure~\ref{fig:mr_arfi_path_axes}).  ARFI was most correlated to MR in the
lateral-to-lateral axis in both the total and central glands (R$^2$ = 0.47 and
0.44, respectively), with mean overestimates of 8.1 $\pm$ 18.4\% and 0.06 $\pm$
17.2\%, respectively (Table~\ref{tab:mr_arfi_axes_error}).  ARFI had very good
correlation with the total prostate gland axis in the anterior-to-posterior
dimension (R$^2$ = 0.58), but poor correlation in the central gland (R$^2$ =
0.00), with overestimates of 17.0 $\pm$ 12.1 and 14.8 $\pm$ 23.1\%.  ARFI
imaging had weak correlation with MR images in the apex-to-base dimension
(R$^2$ = 0.15, total gland and R$^2$ = 0.20, central gland), with differences
of 0.58 $\pm$ 12.9 and -10.8 $\pm$ 22.3\%, respectively.

>>>>

Weights and axis measurements from the gross pathology processing of the
excised prostates were collected (Table~\ref{tab:path_data}), and using the
axis measurements (lateral-to-lateral, anterior-to-posterior, and
apex-to-base), the prostate volume was approximated as a tri-axial ellipsoid,
and its volume was estimated (\ref{eqn:ellipsoid_volume}).  Prostate weights
were moderately correlated with estimated pathology ellipsoidal prostate
volumes (Figure~\ref{fig:mr_arfi_weight}(a), R$^2$ = 0.68).  There was moderate
correlation between the prostate weight and the image-reconstructed prostate
volumes (Figure~\ref{fig:mr_arfi_weight}(b), R$^2$ = 0.44 (MR) and 0.18
(ARFI)), though there was weaker correlation with the ellipsoidal approximation
of the measurement prostate volume and the image-reconstructed volumes
(Figure~\ref{fig:mr_arfi_weight}(c), R$^2$ = 0.08 (MR) and 0.00 (ARFI)).

@@

Measurements of the prostate total and CG dimensions along the three
standard anatomic axes (apex-to-base, lateral-to-lateral, and
anterior-to-posterior) were made (Table~\ref{tab:mr_arfi_axes}), and the
correlation between the imaging axis measurements was analyzed
(Figure~\ref{fig:mr_arfi_path_axes}).  ARFI was most correlated to MR in the
lateral-to-lateral axis in both the total and CG (R$^2$ = 0.57 and
0.32, respectively), with mean overestimates of 13.5 $\pm$ 11.0\% and 11.5 $\pm$
22.5\%, respectively (Table~\ref{tab:mr_arfi_axes_error}).  ARFI had moderate
correlation with the total prostate gland axis in the anterior-to-posterior
dimension (R$^2$ = 0.23), but poor correlation in the CG (R$^2$ =
0.00), with overestimates of 5.7 $\pm$ 20.6 and -8.4 $\pm$ 24.0\%.  ARFI
imaging had weak correlation with MR images in the apex-to-base dimension
(R$^2$ = 0.19, total gland and R$^2$ = 0.09, CG), with differences
of -2.4 $\pm$ 17.0 and 1.2 $\pm$ 19.8\%, respectively.
